---
title: "John Bennett"
output: html_document
date: 'March 30, 2022 '
---

My goal was to translate a famous animation into an animation of different subject matter that I chose. So, I start with the code for Hans Rosling’s awesome animated plot of econ development data by continent. I want to take that code, and animate the relationship between US military deaths and US military suicides, in the period of the Iraq and Afghan wars. 
Note: The animation of the military data begins on line 56 below. 

```{r Packages}
install.packages(c('gapminder','ggplot2','gganimate','gifski'))
```

```{r Gapminder}
library(gapminder)
library(gganimate)
library(ggplot2)
gapminder
df=gapminder
as.data.frame(gapminder)
```


```{r Df to CSV}
library(readr)
write_csv(df, "~/Documents/GitHub/Portfolio2Test/gapfinder_df.csv")
```


```{r Scatterplot}
ggplot(data = df, aes(gdpPercap, lifeExp, size = pop, colour = country)) +
   geom_point(alpha = 0.7, show.legend = FALSE) +
   scale_colour_manual(values = country_colors) +
   scale_size(range = c(2, 12)) +
   scale_x_log10() +
   facet_wrap(~continent) +
   labs(title = 'Year: 1952-2007', x = 'GDP per capita', y = 'Life expectancy')
```
```{r Save plot to file}
ggsave('plot_gdpPercap_lifeExp_static.png', width=8, height=8)
```

```{r Animating}
p1 <- ggplot(gapminder, aes(gdpPercap, lifeExp, size = pop, colour = country)) +
             geom_point(alpha = 0.7, show.legend = FALSE) +
             scale_colour_manual(values = country_colors) +
             scale_size(range = c(2, 12)) +
             scale_x_log10() +
  facet_wrap(~continent) +
             labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'Life expectancy') +
             transition_time(year) +
             ease_aes('linear')
animate(p1)
anim_save('plot_gdpPercap_lifeExp.gif')
```

So far so good. That works! Now to incorporate the death on Soldier deaths and suicides. 




